Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-02 paper/manuscript.Rmd
add R citation

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between Western and Eastern Indian
Islands (Figure 1), a distance of at least 470 m which took ~9 minutes (~52 m
per minute). This observation prompted us to investigate whether swimming
behaviour was common among GPS radio-collared caribou in the population (n = 29
adult females; 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario,
Canada). We identified swimming events as two consecutive GPS locations (2-hour
relocation rates)  from an individual occurred on different islands.
Northeastern Newfoundland typically experiences pack ice during winter and
caribou are known locally to travel between islands by walking over the ice. We
restricted our GPS data to the ice-free period of the year (April 1 - December
31) and we identified `r nids` adult female caribou that collectively had `r nevents` 
swimming events over three years (Figure 2). In addition to our own
visual and remotely sensed observations, residents of Fogo Island have also
reported observing caribou swimming between islands on numerous occasions.

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada, is home to
approximately 300 woodland caribou. During routine fieldwork on May 30, 2017, we
observed an unmarked adult male caribou swim between Western and Eastern Indian
Islands (Figure 1), a distance of at least 470 m which took ~9 minutes (~52 m
per minute). This observation prompted us to investigate whether swimming
behaviour was common among GPS radio-collared caribou in the population (n = 29
adult females; 1240g, GPS 4400M; Lotek Wireless Inc., Newmarket, Ontario,
Canada). Using `r substr(version$version.string, 1, 15)` [@R], we identified swimming events as two consecutive GPS locations (2-hour
relocation rates)  from an individual occurred on different islands.
Northeastern Newfoundland typically experiences pack ice during winter and
caribou are known locally to travel between islands by walking over the ice. We
restricted our GPS data to the ice-free period of the year (April 1 - December
31) and we identified `r nids` adult female caribou that collectively had `r nevents` 
swimming events over three years (Figure 2). In addition to our own
visual and remotely sensed observations, residents of Fogo Island have also
reported observing caribou swimming between islands on numerous occasions.
